---
title: "p8105_hw3_amw2275"
author: "Adam Whalen"
date: "10/10/2020"
output: github_document
---

```{r setup}
library(tidyverse)

## maybe include some global formatting/mapping here ##
```

## Problem 1

```{r}
library(p8105.datasets)
data("instacart")
```

This data set contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. Observations are the level of items in orders by user. There are user/order variables: user ID, order ID, order day, and order hour. There are also item variables: name, aisle, department, and some numeric codes. 

How many aisles, and which are most items from?

```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))
```

Let's make a plot!

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n > 1000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)
  ) %>% 
  ggplot(aes(x = aisle, y = n))+
  geom_point() +
  theme(axis.text = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Let's make a table!

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4) %>% 
  arrange(aisle, rank) %>% 
  knitr::kable()
```

Apples vs ice cream:

```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  )
```

## Problem 2

Import, clean, and wrangle the data set.
```{r}
accel_df = 
  read_csv("data/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    day = as.factor(day)
  ) %>% 
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minute",
    names_prefix = "activity_",
    values_to = "activity"
  ) %>% 
  mutate(
    weekday = if_else(day %in% c("Saturday", "Sunday"), "TRUE", "FALSE"),
    weekday = as.factor(weekday),
    minute = as.numeric(minute)
  ) %>% 
  relocate(week, day_id, day, weekday)
```

Aggregate activity data across days. 

Create a plot to show aggregated activity data by day.







